---
title: "Running Slide"
author: "Vignette Author"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

#### SLIDE paper:

(preprint) <https://www.biorxiv.org/content/10.1101/2022.11.25.518001v1.full.pdf>

Essential Regression is a linear model - to extend this model and account for non-linear relationships, we can use SLIDE. The first step of running SLIDE is to run Essential Regression. SLIDE then uses the latent factors to:

-   determine the significant latent factors using a knockoff approach
-   model interactions between latent factors

The SLIDE package is great and the functions I use to run SLIDE are basically just wrappers that plot things.

### Running SLIDE

The SLIDE package is a dependency of JishnuLabTools and should be loaded when you load this package.

As stated above, the first step to running SLIDE is running ER

## Step 1: Run ER

```{r running_er, include = T, eval = F}

library(devtools)
library(doParallel)
library(foreach)
library(tidyverse)

# if need to install
devtools::install_github(repo = "TranscriptionFactory/JishnuLabTools", force = F, dependencies = T)

library(JishnuLabTools)

cores <-  as.numeric(Sys.getenv('SLURM_CPUS_PER_TASK', unset=NA))
if(is.na(cores)) cores <- detectCores()
# if(!is.na(cores) & cores > 1) cores <- cores
registerDoParallel(cores)
cat('number of cores using', cores, '. . .\n')


yaml_path = 'path_to_your_yaml_file.yaml'

# run Essential Regression
EssReg::pipelineER3(yaml_path)
```

## Step 2: Run SLIDE

Use the same yaml file that you used to generate the ER results (SLIDE requires some of the output files from ER + the input X/Y dataframes)

The output will be placed in the output folder specified in the yaml path.

#### run_slide

For simple analysis of ER results, we just want to know the significant latent factors and don't care about interactions, so we set `do_interacts = F`

The `spec` parameter is a threshold for latent factor significance - higher spec = more stringent, fewer significant latent factors and vice verse.

The `do_interacts` and `spec` arguments are arguments for SLIDE.

```{r running_slide, include = T, eval = F}

JishnuLabTools::run_slide(yaml_path = 'path_to_yaml_file_that_you_used_to_run_ER.yaml', 
                          spec = 0.1, do_interacts = F)
```

#### Output:

-   `sig_genes.RDS` A list of the significant latent factors and associated genes + correlation and latent factor loading information.
-   `slide_res` A list of the significant latent factors: marginal vars (non-interacting), interaction vars, interactions.
-   `z_mat.csv` The latent factor Z matrix.
-   `plotSigGenes.png` The significant genes (by latent factor loading and spearman correlation to Y values), for each significant latent factor.
-   `plotSigGenes_data.RDS` The data used the plot the png.
-   `auc_boxplot.png` Re-plots the ER results as a boxplot with p-values

*the main output you'll want for SLIDE with no interactions is the `plotSigGenes.png` and `pltoSigGenes_data.RDS`. These are processed SLIDE results*
